### 2017-05-12 Paper Drafts/Draft1/Draft1.tex
Results Tables
First Draft: Analysis Results

\begin{table}[ht]
	\tbl{\(\hat{\theta}\) Distribution}
	{
		\begin{tabular}{@{}lcccc@{}} \toprule
			\(n\) & 1 & 2 & 4 & 8  \\ 
			\colrule
			\(\sigma_p \)  & mean (std dev) & mean (std dev) & mean (std dev)  \\
			\(\ell\)  & mean (std dev) & mean (std dev) & mean (std dev)  \\
			\(\sigma_n\)  & mean (std dev) & mean (std dev) & mean (std dev)  \\

			\botrule
		\end{tabular}
	}
	\label{tab::simulation}
\end{table}

@@

>>>>

Removes estimates where \(\ell > 1000\) to stabilise distribution.

\begin{table}[ht]
	\tbl{\(\hat{\theta}\) Distribution}
	{
		\begin{tabular}{@{}cccc@{}} \toprule
			\(n\)  & \(\sigma_p \) & \(\ell\) & \(\sigma_n\) \\
			\colrule
			1 & 1.09 (0.47) & \(10^{14}\) (\(10^{15}\)) & 0.57 (0.54) \\
			2 & 0.97 (0.29) & \(10^{13}\) (\(10^{14}\)) & 0.99 (0.15) \\
			4 & 0.97 (0.25) & 63.66 (136.96) & 1.00 (0.09) \\
			8 & 0.99 (0.24) & 56.21 (48.24) & 1.00 (0.06) \\			
			\botrule
		\end{tabular}
	}
	\label{tab::simulation_option2}
\end{table}

\begin{table}[ht]
	\tbl{\(\hat{\theta}\) Distribution}
	{
		\begin{tabular}{@{}cccc@{}} \toprule
			\(n\)  & \(\sigma_p \) & \(\ell\) & \(\sigma_n\) \\
			\colrule
			1 & 0.46 (0.21) & \(10^{14}\) (\(10^{15}\)) & 0.07 (0.08) \\
			2 &  0.45 (0.20) & 259.18 (309.02) & 0.10 (0.02) \\
			4 & 0.45 (0.20) & 279.50 (363.12) & 0.10 (0.01) \\
			8 & 0.47 (0.21) & 291.61 (343.14) & 0.10 (0.01) \\			
			\botrule
		\end{tabular}
	}
	\label{tab::simulation_option3}
\end{table}

\begin{table}[ht]
	\tbl{\(\hat{\theta}\) Distribution}
	{
		\begin{tabular}{@{}cccc@{}} \toprule
			& \(\sigma_p \) & \(\ell\) & \(\sigma_n\) \\
			\colrule
			Data Generating values & 0.50 & 250 & 0.10 \\
			Full Sample Estimate &  0.41 & 156.75 & 0.10 \\
			Resampled Estimates & 0.42 (0.01) & 161.06 (27.11) & 0.10 (0.01) \\		
			\botrule
		\end{tabular}
	}
	\label{tab::simulation_option4}
\end{table}

@@

\begin{table}[ht]
	\tbl{\(\hat{\theta}\) Distribution}
	{
		\begin{tabular}{@{}cccc@{}} \toprule
			Basis & \(\sigma_p\) & \(\ell\) & \(\sigma_n\) \\
			\colrule
			1 & 0.35 (0.008) & 224.5 (39.15) & 0.08 (0.007) \\
			2 & 0.51 (0.015) & 287.9 (44.76) & 0.09 (0.009) \\
			3 & 0.42 (0.021)& 204.2 (30.39) & 0.08 (0.009) \\
			4 & 0.59 (0.019) & 390.1 (74.44) & 0.14 (0.013) \\
			5 & 0.51 (0.010) & 339.8 (42.81) & 0.08 (0.008) \\
			6 & 0.48 (0.013) & 148.6 (23.29) & 0.09 (0.011) \\
			\botrule
		\end{tabular}
	}
	\label{tab::bat_results_option2}
\end{table}
